\documentclass[a4paper,11pt]{article}

\usepackage{geometry}
\geometry{hmargin=3cm,vmargin=3.5cm}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage[english]{babel}

\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{color}

\usepackage{appendix}

\usepackage{tikz}

%\usetikzlibrary{decorations.pathmorphing}
\usepgflibrary{decorations.pathreplacing}

\usepackage{comment,amsmath,amsthm,amssymb}
\usepackage[noend,linesnumbered]{algorithm2e}

\usepackage[shortlabels]{enumitem} %change the numbers in enumerate

\theoremstyle{definition}
  \newtheorem{definition}{Definition}[section] 
\theoremstyle{definition}
  \newtheorem*{notation}{Notation}
\theoremstyle{remark}
  \newtheorem*{remark}{Remark}
\theoremstyle{plain}
  \newtheorem{theorem}{Theorem}
\theoremstyle{lemma}
  \newtheorem{lemma}[theorem]{Lemma}
\theoremstyle{corollary}
  \newtheorem{corollary}[theorem]{Corollary}
\theoremstyle{definition}
  \newtheorem{ex}{Example}
  
%\renewcommand{\epsilon}{\varepsilon}
  
\begin{document}
  

\title{WP2 - Crowd generation code}
\author{}
\date{}

%\maketitle

\paragraph{Generation of the path}~

\noindent The algorithm of least-effort approach is divided in many points.
\begin{itemize}
  \item Grid arrangement and setting up of the grid.
  \item Computation of the minimum on a graph with the $A*$ algorithm.
  \item Computation of the authorised velocity field.
  \item Finding the exclusion zones in order to do the minisation.
  \item Update of the graph with the attribution of a new weight on the edges: each character affect the weight of its neighbour edges.
\end{itemize}

\noindent We also started coding the classes that we will use:
\begin{itemize}
  \item Graph: describes the graph that was set up, with a set of nodes and a dictionnary of dictionnaries of edges.
  \item Individual: skeleton rigify, includes position, maximal speed, optimal speed, trajectory and some variable to compute the energy.
  \item Crowd: contains a set of indivuduals and the graph.
  \item Environment: gives the set of forbidden regions.
\end{itemize}

\paragraph{Motions of the characters}~



\end{document}
